%!TEX TS-program = xelatex
%\documentclass[print]{friggeri-cv}
\documentclass[]{friggeri-cv}

\begin{document}
\header{elias}{obeid}
    {master of science in computer science and engineering}

% In the aside, each new line forces a line break
\begin{aside}
  \section{about}
    Elias Khazen Obeid
    February, 1991
    ~
    Lakeshore Tower, JLT~(Cluster Y), Dubai
    United Arab Emirates
    %Grøntoften
    %2870 Dyssegård
    %Denmark
    ~
    %\textbf{mobile} +45 71 20 29 91
    +971 50 179 8766
    %\href{mailto:ekobeid@gmail.com}{ekobeid@gmail.com}
    \href{mailto:elias@seez.co}{elias@seez.co}
    \href{mailto:elias@munk.ai}{elias@munk.ai}
    %\href{http://obeid.dk}{http://obeid.dk}
    %\href{https://www.facebook.com/eliaskhazenobeid}{fb://eliasobeid}
    \href{https://github.com/obeyed}{github.com/obeyed}
    \href{https://www.linkedin.com/in/eliasobeid}{linkedin.com/eliasobeid}
  \section{language}
    trilingual danish/english/arabic
  \section{programming, markup, and tools}
    C, C++, C\#, CUDA, Java, JavaScript, Python, Ruby, Lua, 
    SQL, NoSQL, ReQL, 
    Haskell (learning),
    Git, SVN, Docker, Vim, Terminal, \LaTeX{}, Linux, Windows
  \section{main interests}
    cryptology
    machine learning
    computer security
    multi-agent system
    software engineering
\end{aside}

\section{education}

\begin{entrylist}
  \entry
    {2014--2016}
    {M.Sc. {\normalfont Computer Science and Engineering}}
    {The Technical University of Denmark}
    {Four semesters (120 ECTS) of four months each.
	Master thesis with the topic of machine translation and natural language processing.}
  \entry
    {2011--2014}
    {B.Sc. {\normalfont Computer Science}}
    {The University of Aalborg}
    {Six semesters (180 ECTS) of four months each.
	Bachelor project with the topic of genetic algorithms.}
  \entry
    {2007--2010}
    {Student}
    {The Technical Gymnasium of Aalborg}
    {Communication and Media}
%  \entry
%    {1998–2007}
%    {State school pupil}
%    {Mellervangskolen}
%    {0th to 9th grade}
\end{entrylist}

\section{work experience}

\begin{entrylist}
  \entry
    {since 2016}
    {Software engineer}
    {Seez}
    {
      The founder of Seez has a vision of making it easier and more transparent to sell/buy a used car.
      I am mainly in charge of the back-end architecture of the company.
      I re-built the company's API with Flask (a python framework).
      I maintain the servers, the file storage, and DNS, which is hosted by AWS. 
      The API runs inside a Docker container, from which it serves data for the android and iOS apps.
      The API is connected to a RethinkDB database.

      I use Git and Dokku for easy version control and deployment of the API.
      Moreover, in collaboration with my colleagues, we used Scrapy for data crawling.
      With that data we were able to apply machine learning techniques to approximate prices of the used car market.
	  }
%  \entry
%    {since 2016}
%    {Co-founder \& machine learning consultant}
%    {munk.ai}
%    {
%      Startup company (in collaboration with co-authors of master thesis) which will provide API's for image recognition with a mission of providing generalized image recognition.
%    }
  \entry
    {2015--2016}
    {Student developer}
    {Berlingske People A/S, Radio24syv}
    {
      Development of website, API infrastructure, and other IT tools used internally. 
      Mainly development with NodeJS with ExpressJs, AngularJS, and C\#.
      For serving the IT systems we used Heroku and custom local servers.

      Moreover, some other systems had been outsourced to third party contractors.
      On the custom local servers, we used git and Dokku for easy deployment and revision control of the developed code.
      The services were connected to third party data sources along with a local MongoDB database.
    }
  \entry
    {2014--2015}
    {Student developer}
    {Falck Healthcare A/S}
    {
      Development of a booking system for a service, that Falck Healthcare offers its clients. 
      Mainly web development with Ruby on Rails. The booking service stored data in a PostgreSQL database.
    }
  \entry
    {08–12 2013}
    {Assistant teacher}
    {The University of Aalborg}
    {Assistant teacher in imperative programming with C.}
%  \entry
%    {2012--2014}
%    {Ambassador}
%    {The University of Aalborg}
%    {Ambassador for Computer Science}
%  \entry
%    {08–11 2011}
%    {Salesmen}
%    {LN Eurocom}
%    {Sale of news paper over the phone for Nordjyske Stiftstidende}
  \entry
    {02–07 2011}
    {Private (national service)}
    {Danish Emergency Management Agency}
    {Firefighting education and emergency duty.}
%  \entry
%    {2010–2011}
%    {Shop assistant}
%    {Twenty4-7, Aalborg}
%    {Customer service, cleaning, replenishment of stock}
%  \entry
%    {2008–2010}
%    {Shop assistant/driver}
%    {La Pronto Pizza, Aalborg}
%    {Customer service, cleaning, cooking and delivery}
\end{entrylist}

\newpage

\section{publications}

\begin{entrylist}
  \entry
    {Oct 2016}
    {Neural Machine Translation with Characters and Hierarchical Encoding\\}
    {\href{https://arxiv.org/abs/1610.06550}{arxiv.org/abs/1610.06550}}
    {We propose a model for translating between languages with a hierarchical architecture. It is fed with sequences of 
    characters from a source language and produces a translated sequence of characters in a target language.
    We argue that, by comparison to current state of the art models, this hierarchical architecture reduces computational 
    complexity, and that it improves translation performance.}
\end{entrylist}

\section{other activity}

\begin{entrylist}
  \entry
    {2011--2011}
    {Education in Firefighting}
    {Danish Emergency Management Agency}
    {Fire, Rescue, Environment and Communication.}
  \entry
    {2013--2014}
    {Member of the Board of Studies}
    {The University of Aalborg}
    {Discussions of applications of qualifications and exemptions, study lines, quality assurance of education and the like.}
%  \entry
%  {2013}
%  {Set up of website with WordPress}
%  {Emergency Center of Aalborg}
%  {Volunteer work.
%  \textit{The website is no longer in use.}
%  Set up website for the volunteers associated with The Emergency Center of Aalborg.
%  The website was for authorised users where they could sign in, view activity calendar, view images and relevant documents, write stories, and find other relevant information.
%  }
%  \entry
%  {2012 \& 2013}
%  {Rus-instructor}
%  {The University of Aalborg}
%  {Intruktor for new students}
  \entry
    {2012--2014}
    {Volunteer mentor}
    {Danish Red Cross Youth}
    {A project called \href{http://www.urk.dk/solskinsunge/}{Sunshine youth}, with the purpose of motivating youngsters for an education in Aalborg (Denmark).}
%  \entry
%  {2011-2014}
%  {Volunteer firefighter}
%  {Emergency Center of Aalborg}
%  {Maintenance of my firefighting education}
%  \entry
%  {since 2009}
%  {Driver's license}
%  {}{}
\end{entrylist}

\end{document}
